\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev 0 are
NOT included.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 16\\
Felix Hurst & 16\\
Marcos Hernandez-Rivero & 16\\
BoWen Liu & 16\\
Andy Liang & 8\\
\bottomrule
\end{tabular}
\end{table}

Andy has had multiple absences over reading week due to him focusing on a deferred
exam, and later had a family emergency causing a few more absences.

\newpage

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } Dr.\ Stephen Kelly

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Felix Hurst & 3\\
Marcos Hernandez-Rivero & 2\\
BoWen Liu & 3\\
Andy Liang & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Felix Hurst & 1\\
Marcos Hernandez-Rivero & 0\\
BoWen Liu & 0\\
Andy Liang & 0\\
\bottomrule
\end{tabular}
\end{table}

Marcos attempted to attend the lecture as well, but accidentally went to the wrong
lecture hall and missed the lecture as a result.

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } Tanya Djavaherpour

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Felix Hurst & 1\\
Marcos Hernandez-Rivero & 1\\
BoWen Liu & 1\\
Andy Liang & 0\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 84 & 100\% \\
Felix Hurst & 27 & 32\% \\
Marcos Hernandez-Rivero & 22 & 26\% \\
BoWen Liu & 31 & 37\% \\
Andy Liang & 4 & 5\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Felix Hurst & 22 & 0 \\
Marcos Hernandez-Rivero & 9 & 0 \\
BoWen Liu & 13 & 0 \\
Andy Liang & 5 & 0 \\
\bottomrule
\end{tabular}
\end{table}

Our team members have been creating issues for their own tasks, and then
closing them when finished. The peer and TA review for the VnV Report and Extras
will be the last issues we will close that would fall under Assigned (C only),
which we will get to some time between now and April 6th.

\section{Team Charter Trigger Items}

Summary of triggers:
\begin{itemize}
    \item A team member misses a meeting without notice.
    \item A team member ignores Discord server messages for more than 24 hours.
    \item A team member contributes less than 20\% of the total commits, issues closed, and other administrative tasks.
\end{itemize}

Andy missed 4 of our meetings in the period of interest without proper notice.
These incidents occurred on February 28th, March 14th, 19th and 24th.
Andy has also been failing to make frequent commits to the repository as
requested, and has contributed less than 20\% of the total commits, issues closed,
and other administrative tasks.

We have been patient with Andy regarding his deferred exam and family emergency,
and have been tasking him with non-critical features, to ensure the project could
continue development at a steady pace, despite Andy's inconsistent participation during
the period of interest.

\newpage

\section{Additional Productivity Metrics}

One additional metric we have is the message history in our Discord server,
showing how active each team member is in asynchronous, text-based communication.
The table below records the number of text messages sent to our server in the period
of interest. This data was recorded on 2026--03--25 at 6:00 PM EST.\\

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Discord Chat Messages}\\
\midrule
Felix Hurst & 537\\
Marcos Hernandez-Rivero & 295\\
BoWen Liu & 360\\
Andy Liang & 91\\
\bottomrule
\end{tabular}
\end{table}

\end{document}