\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

The proof of concept will be a specially curated sandbox level with a player controlled character and sample environment which contains objects that highlight the functionality of player’s tools and mold traversal. In terms of our demonstration of the slime mold, it will be represented by a segmented game object, such as a plant or fungus. The player can manipulate the terrain to unearth some water. The slime mold will then react by traversing closer to the water source. Other similar environmental manipulations may be involved in this demonstration, such as heat and light sources, which also cause the slime mold to react in different ways.\\

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 6\\
Felix Hurst & 6\\
Marcos Hernandez-Rivero & 6\\
BoWen Liu & 6\\
Andy Liang & 5\\
\bottomrule
\end{tabular}
\end{table}

Andy was unexpectedly busy during one of the meetings.\\


\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: Dr. Stephen Kelley}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Felix Hurst & 2\\
Marcos Hernandez-Rivero & 2\\
BoWen Liu & 1\\
Andy Liang & 2\\
\bottomrule
\end{tabular}
\end{table}

BoWen was unexpectedly busy during one of the meetings.\\

\section{Lecture Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Felix Hurst & 11\\
Marcos Hernandez-Rivero & 10\\
BoWen Liu & 0\\
Andy Liang & 0\\
\bottomrule
\end{tabular}
\end{table}

Andy does not attend lectures because he lives in Toronto and only has two courses this term, making commuting to Hamilton not worth his time. BoWen does not attend lectures because he lives in Mississauga and commuting to Hamilton is too costly for him.\\

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: Tanya Djavaherpour}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Felix Hurst & 3\\
Marcos Hernandez-Rivero & 3\\
BoWen Liu & 3\\
Andy Liang & 3\\
\bottomrule
\end{tabular}
\end{table}

Felix and Marcos attend TA meetings in person. BoWen and Andy attend TA meetings virtually, joining Discord calls connected through Marcos and/or Felix’s laptop(s).

\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 56 & 100\% \\
Felix Hurst & 10 & 18\% \\
Marcos Hernandez-Rivero & 21 & 38\% \\
BoWen Liu & 38 &68 \% \\
Andy Liang & 29 & 52\% \\
\bottomrule
\end{tabular}
\end{table}

A decent amount of co authored commits covers pretty much only when the PDF and .tex files are first pushed to git. Marcos is the primary individual that transfers all of the writing from a shared google docs to the LaTeX files, and often has to commit several times to make changes or fix issues where it won't compile into a PDF. BoWen, Andy, and Marcos, but moreso BoWen, have a tendency of committing a large amount of very small changes whenever they edit a document, instead of going through it once, fixing the changes and then committing just those changes. Felix does not have this tendency, but the amount of work he contributes in terms of lines written, parts done, and documents reviewed does match up to everyone elses, and we can all vouch for this.\\

Also as an extra note, when doing the commits, we forgot to co author them properly, so Marcos had to go in and rebase the repo, which is why every file looks like it has recent changes and the commits are all committed by Marcos (though this was accounted for when declaring his commit contributions, what you see in the table is what he actually did in terms of work.)\\

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Felix Hurst & 6 & 0\\
Marcos Hernandez-Rivero & 6 & 2\\
BoWen Liu & 2 & 2\\
Andy Liang & 2 & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}

Continuous integration is implemented with updates on each member’s area of specialization (libraries, and functions) with team code standups and code reviews.\\

In terms of testing, our team will be extensively testing each technology separately in specially designed unit tests after each update. Continuous integration will involve unit test, security, and formatting checks.\\


\section{Team Charter Trigger Items}

Summary of triggers:\\
	- A team member misses a meeting without notice.\\
	- A team member ignores Discord server messages for more than 24 hours.\\
	- A team member contributes less than 20\% of the total commits, issues closed, and other administrative tasks.\\

A team member missed a meeting without notice on October 21st. They later explained they were mistakenly not getting notifications on Discord. This violation was considered minor and was forgiven immediately, with the expectation that the team member would take more care with their notification settings and personal reminders in the future.\\


\section{Additional Productivity Metrics}

One additional metric we have is the message history in our Discord server, showing how active each team member is in asynchronous, text-based communication. The table below records the number of text messages sent to our server in the period of interest. This data was recorded on 2025-11-03 at 7:45 PM EST.\\

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Discord Chat Messages}\\
\midrule
Felix Hurst & 556\\
Marcos Hernandez-Rivero & 421\\
BoWen Liu & 357\\
Andy Liang & 234\\
\bottomrule
\end{tabular}
\end{table}


\end{document}