\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\section{Demo Plans}

Our team plans to demonstrate a fully functional level of our project.
This will feature all the core mechanics of the project, including the player
movement, tool usage, destructible environment, and the slime mold organism.
The level will feature some simple puzzles to overcome to progress from left to right.
These puzzles will require interaction with the slime mold organism, showcasing the
key goal of our project, to explore the slime mold algorithm, teach the players about it,
and evoke emotions such as curiosity and hope from our player.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 7\\
Felix Hurst & 7\\
Marcos Hernandez-Rivero & 7\\
BoWen Liu & 7\\
Andy Liang & 6\\
\bottomrule
\end{tabular}
\end{table}

\newpage

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } Dr. Stephen Kelly

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Felix Hurst & 2\\
Marcos Hernandez-Rivero & 2\\
BoWen Liu & 2\\
Andy Liang & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Felix Hurst & 1\\
Marcos Hernandez-Rivero & 0\\
BoWen Liu & 0\\
Andy Liang & 0\\
\bottomrule
\end{tabular}
\end{table}

Team members who were absent from the lecture were at work.

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } Tanya Djavaherpour

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Felix Hurst & 1\\
Marcos Hernandez-Rivero & 1\\
BoWen Liu & 1\\
Andy Liang & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 21 & 100\% \\
Felix Hurst & 9 & 42.9\% \\
Marcos Hernandez-Rivero & 2 & 9.5\% \\
BoWen Liu & 9 & 42.9\% \\
Andy Liang & 1 & 4.7\% \\
\bottomrule
\end{tabular}
\end{table}

Marcos and Andy have recently been working locally and on unmerged branches.
We believe the technical contributions have been relatively balanced despite
the drastic differences in number of commits to the main branch from the PoC
demo to now.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Felix Hurst & 11 & 7 \\
Marcos Hernandez-Rivero & 3 & 9 \\
BoWen Liu & 8 & 11 \\
Andy Liang & 1 & 2 \\
\bottomrule
\end{tabular}
\end{table}

Felix is responsible for creating and closing issues that track meeting attendance.
Andy has low activity in the issue tracker due to the large workload associated with
the slime mold integration, which has been tracked by only one issue in the repository.

\section{CICD}

C\# scripts used in the Unity project undergo automated unit testing in the repository under
\verb|Game-Files/test/|. This will ensure the foundational functions in our scripts are verified.

\newpage

\section{Team Charter Trigger Items}

Summary of triggers:
\begin{itemize}
    \item A team member misses a meeting without notice.
    \item A team member ignores Discord server messages for more than 24 hours.
    \item A team member contributes less than 20\% of the total commits, issues closed, and other administrative tasks.
\end{itemize}

Andy missed a meeting on January 22nd and did not provide a good reason for it,
he said he simply forgot about it.
We will be providing more reminders to the team to prevent members from
forgetting about meetings. Andy will be spoken to more seriously if this
behaviour continues.

\section{Additional Productivity Metrics}

One additional metric we have is the message history in our Discord server,
showing how active each team member is in asynchronous, text-based communication.
The table below records the number of text messages sent to our server in the period
of interest. This data was recorded on 2026-01-29 at 12:00 PM EST.\\

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Discord Chat Messages}\\
\midrule
Felix Hurst & 257\\
Marcos Hernandez-Rivero & 132\\
BoWen Liu & 135\\
Andy Liang & 81\\
\bottomrule
\end{tabular}
\end{table}

\end{document}