
\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{5cm}p{2cm}X}
\toprule {\bf Author} & {\bf Version}& {\bf Date}\\
\midrule
All & 1.0 & November 2026\\
Marcos Hernandez-Rivero & 1.1 & November 2026\\
Marcos Hernandez-Rivero & 1.2 & December 13, 2026\\
Felix Hurst & 1.3 & February 26, 2026\\
Felix Hurst & 1.4 & March 4, 2026\\
\bottomrule
\end{tabularx}

\newpage

\tableofcontents
\newpage
\listoftables
\newpage

\pagenumbering{arabic}

This document will cover our team's plan to ensure our project will do what we intend it to do,
and will meet our stakeholders' needs. This will cover background information regarding our
software project and team, high-level plans for verifying all the important artifacts of
our project, detailed descriptions of system and unit tests, and lastly, a list of usability
survey questions.

\section{General Information}

This section covers key background information related to the project.

\subsection{Summary}

The software being tested is our game, Ad Natura. This 2D pixel art styled puzzle platformer will take a player on a short adventure through a few levels with environmental puzzles to solve. Two key functions that will be the subject of much verification and validation testing will be the function of destroying and decomposing terrain into small pixel chunks, and the function of the slime mold organism traversing through the area and reacting to environmental stimuli.

\subsection{Objectives}

This project's key objectives include:

\begin{itemize}
\item Establish confidence in software correctness for the primary two functions: Terrain decomposition and the slime mold organism.
\item Establish confidence in software safety and security by ensuring the application maintains system integrity, mitigates vulnerabilities against external exploits, and operates within resource constraints to prevent system instability.
\item Demonstrate our message of cooperation between humans and nature, through the use of aesthetics and environmental storytelling.
\item Demonstrate satisfactory usability for both gamers and non-gamers, to expand to a wide audience.
\end{itemize}

\noindent Objectives that are out of scope for this project include:

\begin{itemize}
\item Establishing confidence in software correctness for fundamental Unity engine code and functions. This is not necessary as we can assume that Unity’s engine has been thoroughly verified.

\item Demonstrating eye-catching, memorable visuals and music. These aspects are only important for marketing purposes, which is a very late--stage concern, and therefore not within the scope of this project at this stage.
\end{itemize}

\subsection{Extras}

The extras include a Technical Report on the Slime Mold Algorithm and a Usability Report.
The Technical Report will detail the unique and queer features of slime mold organisms, and
how we were able to implement some of these features into our project.
The Usability Report will take data collected from stakeholder testers to assess the
usability of our system and determine any potential improvements that could be made.

\subsection{Relevant Documentation}

Relevant documents include:

\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/ProblemStatementAndGoals/ProblemStatement.pdf}{\bf{Problem Statement and Goals}}. This document includes information about our goals, which is what the Verification and Validation Plan’s objectives are based on. It also lists stakeholders, which are relevant to our testing efforts.

\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{\bf{Development Plan.}} This document describes our plan for our Proof of Concept Demonstration, which again highlights our most important objectives.

\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/SRS/SRS.pdf}{\bf{Software Requirements Specification.}} This document details all of the requirements, most of which will be subject to verification.

\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/HazardAnalysis/HazardAnalysis.pdf}{\bf{Hazard Analysis.}} This document includes some safety and security focused software requirements, which will be subject to verification.

\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/Design/SoftArchitecture/MG.pdf}{\bf{Module Guide.}} This document describes all of the modules of our system. This is important for organizing our System and Unit Tests.

\section{Plan}

\subsection{Verification and Validation Team}

\begin{table}[H]
\caption{Verification \& Validation Team}
\begin{tabular}{|p{2cm}|p{2cm}|p{6cm}|p{2.5cm}|p{2cm}|}
\hline
\textbf{Name}           & \textbf{Role} & \textbf{Task}                                                                                                                                                                            & \textbf{Primary Section(s)}   & \textbf{Secondary Section(s)} \\ \hline
Felix Hurst             & Author        & Team leader, focuses on keeping all data organized and spearheading meetings about testing with supervisor and other testers. Manages issue tracker. Secondary reviewer to all documents & N/A                           & All                           \\ \hline
BoWen Liu               & Author        & Primary Reviewer for engine and tool system. Secondary reviewer for art direction and environment direction.                                                                             & Game Engine \& Physics        & Art \& Environment            \\ \hline
Andy Liang              & Author        & Primary Reviewer for Art, Environment, and Music systems. Secondary reviewer for all documents.                                                                                          & Art,  Environment, Music      & All                           \\ \hline
Marcos Hernandez-Rivero & Author        & Primary reviewer for Unit testing and static analysis system, ensuring the systems are functional and up to date. Secondary reviewer for all docs.                                       & Unit Testing, Static Analysis & All                           \\ \hline
Stephen Kelley          & Supervisor    & Capstone Supervisor, ensuring we are on track with the theme of the project, and serving as a reviewer for document completeness and correctness.                                        & All                           & N/A                           \\ \hline
Michelle Bunton         & Supervisor    & Aid to the capstone supervisor, ensuring verification and validation of specific elements, such as the slime mold algorithm, are properly done.                                          & All                           & N/A                           \\ \hline
\end{tabular}
\end{table}


\subsection{SRS Verification}

We intend to use a mix of feedback from fellow team members, classmates, and our supervisors.
This will be done via team meetings, supervisor meetings, and peer reviews. Internally,
team members will use an ad hoc feedback approach to log any issues concerning clarity
or consistency in our central issue tracker. For our supervisor, we will conduct informal meetings
where we will discuss the progress on our documentation and ask for their feedback and suggestions,
especially considering complex requirements related to environment manipulation, physics
simulations, and various elements of our project, such as the slime mold algorithm
that we are using, focusing on their feasibility and testability. This ensures we leverage
our supervisor's expertise beyond a simple read-over. Peer reviews with other Capstone teams
will give us further insight into potential flaws in our documentation that we may not be able
to see on our own.

\begin{table}[H]
\caption{SRS Verification Checklist}
\begin{tabular}{|p{4cm}|p{11cm}|}
\hline
\textbf{Criteria} & \textbf{Description}                                                                                                                                                                \\ \hline
Completeness      & Are all necessary functional and non-functional requirements (performance, usability, etc.) documented?                                                                             \\ \hline
Correctness       & Does each requirement accurately reflect the intended system and stakeholder needs?                                                                                                 \\ \hline
Clarity/Ambiguity & Is each requirement stated unambiguously, with a single interpretation? (e.g., avoid words like "good," "usually," "robust")                                                        \\ \hline
Consistency       & Are all requirements consistent with each other, and are terms/definitions used uniformly throughout?                                                                               \\ \hline
Verifiability     & Can a test procedure (inspection, test, demonstration) be designed to verify this requirement? (e.g., "The game must run at 60 FPS" is verifiable; "The game must be fast" is not). \\ \hline
Feasibility       & Can the requirement be achieved with available technology, resources, and schedule?                                                                                                 \\ \hline
Traceability      & Is each requirement uniquely identified to allow tracing to design and test cases?                                                                                                  \\ \hline
\end{tabular}
\end{table}

\subsection{Design Verification}

Our design verification plan focuses on ensuring the architectural and detailed design
correctly implements the SRS and follows good software engineering principles, such as modularity.
The core of this verification will be informal reviews among our team and with our supervisors.
Classmates will be leveraged as peer reviewers to ensure the design is robust and maintainable.
The review process will involve a walk-through of our design documentation, and it will focus
on whether the design efficiently supports all functional requirements for traversing and
manipulating the puzzle environments.

\begin{table}[H]
\caption{Design Verification Checklist}
\begin{tabular}{|p{4cm}|p{11cm}|}
\hline
\textbf{Criteria} & \textbf{Description}                                                                                                                                                                \\ \hline
Traceability to SRS      & Does the design cover every requirement in the SRS, and is all design justified by a requirement?
 \\ \hline
Modularity \& Coupling       & Are components (classes, modules) logically grouped, and is the dependency/communication between them minimal and clearly defined?
\\ \hline
Interface Specification &Are all internal and external component interfaces (APIs, data structures) fully and correctly defined?
\\ \hline
Error Handling       & Are potential error conditions (e.g., resource limit reached, invalid input) identified, and is a recovery/reporting mechanism defined in the design?
\\ \hline
Performance/Resource     & Does the design approach (e.g., algorithm choice, data structure) meet critical non-functional requirements like frame rate and memory usage? 
\\ \hline
Maintainability       & Is the design simple, consistent, and easy to modify or extend without causing unintended side effects?                                                                                                 \\ \hline
\end{tabular}
\end{table}

\subsection{Verification and Validation Plan Verification}

We will subject this document to a peer review by classmates, ensuring the plan adequately
covers verification for all key project artifacts (SRS, Design, Implementation) and specifies
a viable strategy for testing and validation. Additionally, we will employ conceptual
mutation testing by deliberately considering how the plan would handle various types of failures
(e.g., unit test failure, non-functional requirement breach). We will
also subject this document to a review by Dr.\ Kelly and Michelle Bunton, to ensure that the core
ideas and themes of the game, which may not be understood by classmates, are conveyed
properly and free from errors in the document, as well as proper testing mechanisms for
aspects which cannot be unit tested, like the slime mold algorithm.


\begin{table}[H]
\caption{Verification and Validation Plan Checklist}
\begin{tabular}{|p{4cm}|p{11cm}|}
\hline
\textbf{Criteria} & \textbf{Description}                                                                                                                                                                \\ \hline
Scope Coverage      & Does the V\&V plan address verification for all major documents (such as SRS, design, code, etc) and all requirements (FR, NFR)?
 \\ \hline
Method Suitability       & Are the chosen methods appropriate for the documents being verified?
\\ \hline
Resource Allocation &Are the necessary tools, personnel (reviewers, testers), and time for each V\&V activity specified and feasible?
\\ \hline
SMA Testing       & Does the plan specifically address the unique challenges of testing non-deterministic behavior like the SMA?
\\ \hline
Acceptance Criteria     & Does the plan clearly define the Pass/Fail criteria for system validation (e.g., what metrics define acceptable frame rate, or successful puzzle completion)? 
\\ \hline
\end{tabular}
\end{table}

\subsection{Implementation Verification}

This verification relies on two components: manual testing, and
static analysis. We will execute all manual tests detailed in Section~\ref{systemtests}
and Section~\ref{unittests}, covering critical logic like physics calculations and
tool-effect application, that can be mathematically verified. For these tests, we need
to ensure that the game components connect well, and that the goals we set are being met
such as framerate, graphics, tools working properly under different conditions, etc.
For static verification, the team will conduct internal code
inspections on complex components, such as the logic for object mutation. 

%\subsection{Automated Testing and Verification Tools}

%Our team will be using a combination of runtime and CI/CD tests to test each of our
%feature modules. For runtime tests, we will be using Unity's built-in Test Framework
%to create and run unit tests for our core game mechanics, such as proper geometry and
%clipping detection for the terrain destruction system, and slime mold traversal algorithm
%location and logic checking. These tests will be executed locally by developers during
%development to catch issues early. In terms of CI/CD tests, we will integrate automated
%unit tests into our GitHub Actions pipeline. This will ensure that every code
%change is automatically verified for functionality before being
%merged into the main branch. Additionally, we will use Unity's Profiler to monitor
%performance metrics during gameplay, ensuring that non-functional requirements like
%frame rate and memory usage are consistently met.

\subsection{Automated Testing and Verification Tools}
It has been determined that automated testing in the form of continuous integration /
continuous deployment (CI/CD) is not feasible for this project. This is due to the
inaccessibility of Unity Unit Testing integration to GitHub Actions. Unity C-Sharp scripts
require access to the Unity library, which we could not successfully implement while
running the scripts via GitHub Actions. We have determined that it is not a valuable
use of our time to continue to pursue setting up automated testing, and will instead
continue with only manual testing.

\subsection{Software Validation}

We will use the PoC and Rev 0 demos as the first key opportunity for
software validation, ensuring the core functionality aligns with our stakeholders' expectations.

We will also distribute an alpha version of our project to some of our friends, family, classmates,
and other potential testers. These testers will be asked to play through the game and then fill in
a survey form which will ask them questions about their experience with the game.
This survey will act as our Usability Survey, which will be used to write our
Usability Report, as one of our extra deliverables. Usability Survey questions are detailed in
Section~\ref{Survey}.

\section{System Tests}\label{systemtests}
System tests provide an effective and quantifiable way of evaluating success of functional
and non-functional requirements.

\subsection{Tests for Functional Requirements}
The following are tests for the functional requirements outlined in the SRS.
Testing for functional requirements will include the two key game mechanics of
the destructible environment and the slime mold algorithm.
Each feature and mechanic's specific functionalities will be tested to ensure
it meets proper adherence to functionality.

\subsubsection{ObjectDestructionTest-FRT01}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: Character at beginning of level, with a destructible
obstacle in their path.

\textbf{Input}: Select destructive ball tool, approach a destructible obstacle, aim,
and fire the tool at the object.

\textbf{Output}: A destructive ball is fired from the tool at the object.
About one second after contact, the object breaks into smaller pieces.

\textbf{Test Case Derivation}: This test covers the usage of the destructive ball
tool, as well as the destruction of objects themselves, integrated together. This
represents a key game mechanic, as it will be required to damage obstacles in this way
to open a path forward or to uncover useful things trapped behind destructible objects.


\subsubsection{SlimeMoldFunctionalityTest-FRT02}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: Character at beginning of level, with a wood obstacle
in their path, and a slime mold source near that obstacle.

\textbf{Input}: Select water ball tool, approach a wood obstacle, aim,
and fire the tool at the object.

\textbf{Output}: A water ball is fired from the tool at the object.
After making contact with the wood obstacle, a nearby slime mold organism
begins to traverse toward it. After a while, the slime mold decomposes the
wood obstacle, destroying it entirely.

\textbf{Test Case Derivation}: This test covers the usage of the water ball
tool, as well as the slime mold in its basic functionality. The slime mold
will be attracted to the wood obstacle after water is splashed on it. It will
then decompose the wood when it comes into contact with it. This represents a key
game mechanic, as it will be required to use water to guide the slime mold to
decompose obstacles and open a path forward.


\subsubsection{SlimeSporeSpreadingTest-FRT03}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: Character standing still, large number of spore
particles spawned on the ground.

\textbf{Input}: Select spore fan tool, aim at the spore particles on the
ground, and fire the tool at the spore particles.

\textbf{Output}: Spore particles are accelerated away from the character,
following a smooth, gentle path through the air, and landing on the ground
a short distance away. Where spores land, they spawn new slime mold sources.

\textbf{Test Case Derivation}: This test covers the usage of the spore fan
tool, as well as the functionality of the slime mold's reproduction cycle.
This represents a key game mechanic, as it will be required to use the fan
to push spores long distances to spread slime mold to more desirable locations,
for instance, nearer to a wood obstacle.


\subsubsection{SlimeWallClimbTest-FRT04}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: Character at beginning of level, with a vertical
surface (i.e.\ a wall) in their path, and a slime mold source near that wall.

\textbf{Input}: Select water ball tool, aim at the wall, and fire
the tool at the wall. Wait a few seconds, then attempt to climb the wall.

\textbf{Output}: The slime mold is attracted to the water on the wall. After covering
enough of the wall, the wall becomes climbable, and the character ascends it successfully.

\textbf{Test Case Derivation}: This test covers the usage of the water ball tool again,
this time in the context of climbing a wall, another key game mechanic used to overcome
obstacles in the player's path.


\subsection{Tests for Non-Functional Requirements}
The following are tests for the non-functional requirements outlined in the SRS.


\subsubsection{PerformanceTest-NFRT01}

\textbf{Type}: Non-Functional, Dynamic, Manual

\textbf{Initial State}: Freshly loaded level.

\textbf{Input}: Repeated usage of tools in an attempt to spawn as many particles
as possible and/or break obstacles into as many pieces as possible.

\textbf{Output}: The frame rate will be carefully observed, and
should stay within reasonable bounds, averaging 30 fps or higher.

\textbf{Test Case Derivation}: The frame rate is an important measure of
performance for our project. Slow frame rates means an unenjoyable experience.


\subsubsection{SlimeMoldRandomnessTest-NFRT02}

\textbf{Type}: Non-Functional, Dynamic, Manual

\textbf{Initial State}: Freshly loaded level.

\textbf{Input}: Repeated reloads of a single part of a level, each time aiming
the water ball tool in the same place to direct the slime mold toward the first
wood obstacle.

\textbf{Output}: The slime mold should have subtly different, random behaviour each time.

\textbf{Test Case Derivation}: The randomness of the slime mold algorithm
reflects its nondeterminism and organic nature. This is a key aspect of the
slime mold algorithm that we want to demonstrate through our project.


\subsection{Traceability Between Test Cases and Requirements}

The following is a table for the test cases as they relate to the requirements.

\begin{table}[H]
\begin{tabular}{|l|l|}
\hline
\textbf{Requirement Name} & \textbf{Test Cases}  \\ \hline
Destructible Environment  & FRT01        \\ \hline
Slime Mold Traversal      & FRT02, FRT03, FRT04, NFRT02        \\ \hline
Performance               & NFRT01 \\ \hline
\end{tabular}%

\end{table}

\section{Unit Tests}\label{unittests}

\subsection{Unit Testing Scope}

Unit tests will focus on verifying individual modules and functions in isolation.
The scope includes testing core game mechanics, physics calculations,
and algorithm implementations.

\subsection{Tests}

\subsubsection{RaycastObjectSplitTest-UT01}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: Rectangular object.

\textbf{Input}: Apply raycast through object, entering from one side and exiting
out the other, with a straight line.

\textbf{Output}: Remove chunk from object and generate it as a new separated object,
with the shape determined by the placement of the raycast.

\textbf{Test Case Derivation}: This tests the correctness of the calculations that
split an object into multiple pieces after using a tool to break it apart.


\subsubsection{WaterLimitTest-UT02}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: An empty, enclosed area of terrain.

\textbf{Input}: A water spawner is placed inside this area.

\textbf{Output}: Water falls from the spawner and pools up on the ground,
but only to a certain capacity, after which it remains a steady volume
of water directly above the ground.

\textbf{Test Case Derivation}: This tests the correctness of the calculations
that prevent water from pooling up indefinitely and flooding an entire level.


\subsubsection{SlimeMoldAttractionTest-UT03}

\textbf{Type}: Functional, Dynamic, Manual

\textbf{Initial State}: Slime mold source in a relatively stationary state.

\textbf{Input}: Introduction of water particles near slime mold source.

\textbf{Output}: Some slime mold agents begin to move toward the water source.

\textbf{Test Case Derivation}: This tests the correctness of the slime mold
algorithm in terms of movement towards positive incentive sources such as water.


\subsection{Traceability Between Test Cases and Modules}
\begin{table}[H]
\caption{Unit Test to Module Traceability}
\begin{tabular}{|p{2cm}|p{6cm}|p{7cm}|}
\hline
\textbf{Test ID} & \textbf{Module} & \textbf{Purpose} \\ \hline
UT01 & Geometric Operations (M10) & Verify object reshape calculations \\ \hline
UT02 & Attraction Source (M18) & Verify water limit calculations \\ \hline
UT03 & Slime Mold Manager (M17) & Verify attraction source calculations \\ \hline
\end{tabular}
\end{table}

\section{Appendix}

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC CONSTANTS. Their values are defined in this section for easy maintenance.

The following symbolic constants are referenced by system and non-functional tests (Sec. 4). Centralizing them here keeps test cases consistent if values change.

\begin{table}[H]
\caption{Symbolic Parameters}
\begin{tabular}{|p{6.5cm}|p{3.5cm}|p{4.5cm}|p{2cm}|}
\hline
\textbf{Symbol}              & \textbf{Definition}                                 & \textbf{Value/Domain}                                                                                   & \textbf{Referenced Tests} \\ \hline
SAVE\_ON\_DESTROY\_COUNT     & Objects destroyed (precondition) before manual save & 2                                                                                                       & FRTO1                     \\ \hline
AUTOSAVE\_PICKUP\_COUNT      & Objects picked up to trigger auto-save              & 2                                                                                                       & FRTO2                     \\ \hline
SAVE\_RECORD\_FIELDS         & Fields persisted in a save snapshot                 & \{PLAYER\_COORDS, PLAYER\_INVENTORY, PLAYER\_ATTRIBUTES, WORLD\_STATE, GAME\_OBJECTS, LEVEL\_LOCATION\} & FRTO1, FRTO2              \\ \hline
MATERIAL\_TYPES              & Object attribute classes for destruction tests      & \{SOFT, BRITTLE, HARD\}                                                                                 & FRTO3                     \\ \hline
SLIME\_MOLD\_OBSTACLE\_COUNT & Rectangular obstacles in path-traversal level       & 5                                                                                                       & FRTO4                     \\ \hline
TERRAIN\_GAP\_COUNT          & Terrain gaps in path-traversal level                & 1                                                                                                       & FRTO4                     \\ \hline
SLIME\_MOLD\_ATTRACTANT      & Target resource guiding traversal                   & WATER\_DEBRIS                                                                                           & FRTO4                     \\ \hline
\end{tabular}%
\end{table}




Notes: SAVE\_RECORD\_FIELDS mirrors the save--snapshot contents described in the save tests; “LEVEL\_LOCATION” denotes the level/area identifier distinct from PLAYER\_COORDS.
\subsection{Usability Survey}\label{Survey}

\subsubsection{Survey Administration}

All players will submit their automatically generated game report outlining their hardware specifications, performance timeline, and necessary interactions history.

For scaling questions (to what extent, to what degree, etc.), a 5-point Likert scale will be used (1=Strongly disagree ... 5=Strongly agree).

\subsubsection{Preliminary Survey - Demographics}

\begin{itemize}
  \item Games that the user plays (by genre), how much of each genre they generally play (hours/week)
  \item What themes do you enjoy in games that you have played?
  \item Country of origin
  \item Age
  \item Gender
\end{itemize}

\subsubsection{Learnability Section}

\textbf{Overall Completion Time}

\begin{itemize}
  \item How long did it take to clear the game (or a specific level)? \textit{(Note: Edit later based on how many levels we actually end up implementing.)}
\end{itemize}

\textbf{Game Mechanic Learning Curves}

Group by game mechanic and ask about learning curve time with questions specific to that mechanic:

\begin{itemize}
  \item How long did it take before you felt comfortable with that mechanic?
  \item Evaluate the destructible environment on learnability: Was it too unpredictable? Were you able to harness it to clear levels and solve puzzles?
  \item How long did it take until you felt comfortable interacting with the slime mold?
  \item How long did it take you to get used to the control scheme for this game?
\end{itemize}

\textbf{Puzzle Fairness}

\begin{itemize}
  \item When solving a puzzle, did you feel like the solution was fair and logical?
\end{itemize}

\subsubsection{Entertainment Value}

\begin{itemize}
  \item What part(s) of the game did you enjoy the most?
  \item What part(s) of the game did you find frustrating?
  \item How would you rate each mechanic in contributing to the entertainment value of the game?
  \begin{itemize}
    \item Erosion
    \item Breakable objects
    \item Debris generation / Landslides
    \item Water simulation
    \item Slime mold pathfinding
    \item Slime mold as a traversable object
  \end{itemize}
  \item For each level, please leave comments on what is: A) Entertaining, and B) Tedious
\end{itemize}

\subsubsection{Game Business Requirements}

\textbf{Controls \& Intuitiveness}

\begin{itemize}
  \item Do you believe the control scheme was intuitive?
\end{itemize}

\textbf{Performance Issues}

\begin{itemize}
  \item Did you experience any of the following performance issues? (Accompanied with report)
  \begin{itemize}
    \item Frame drops
    \item Input delay
    \item Crashes
    \item Screen freezes
    \item Corrupted save data
  \end{itemize}
\end{itemize}

\textbf{Feedback \& Clarity}

\begin{itemize}
  \item Did you feel that the visual effects, interfaces, and sound design were effective in giving cues and feedback for your performed actions, player state, as well as environmental events?
\end{itemize}

\textbf{Value Proposition}

\begin{itemize}
  \item Did you feel like the game was worth the time you spent playing it?
\end{itemize}

\subsubsection{Story Review / Message}

\begin{itemize}
  \item What message did you believe this game was sending?
  \item What led you to believe this?
  \item Do you agree with the message you believe the game was sending? Why or why not?
  \item Did you believe the game conveyed the message effectively?
  \item Was messaging in the game too upfront, too subtle, or somewhere in the middle?
\end{itemize}

\subsubsection{Emotions}

\begin{itemize}
  \item What were the most common emotions you felt while playing the game?
  \item How did you generally feel at the beginning of the game / Level 1?
  \item How did you generally feel at the end of the game / final level?
  \item Were there any moments that evoked a strong emotion from you? If so, what moment was it, and how did you feel?
\end{itemize}

\subsubsection{Exploring Slime Mold Algorithm (SMA)}

Throughout the game, the player will encounter pop-up tutorial messages explaining various aspects of the Slime Mold Algorithm that are pertinent to game mechanics. For instance, ``The slime mold will be attracted to water. Try uncovering a water source.'' Afterwards, they have the freedom to explore that game mechanic and interact with the slime mold.

NOTE: Some questions may be changed or added as we get further into level design and have a better understanding of what more specific things we are hoping our players will experience and learn.

\textbf{SMA Learning \& Understanding}

\begin{itemize}
  \item What did you learn about slime mold through the game?
  \item How well does the tutorial make clear to you the core mechanics of the slime mold?
  \item Did you feel like the slime mold traversal felt natural and unpredictable?
  \item How do you feel about the balance of level design, triggerable objects, and destructible objects in terms of the interaction of the slime mold with those elements?
  \item Do you consider the slime mold to be an ally, enemy, or neutral party?
  \item What questions do you still have about slime mold?
  \item Overall, what do you think is the most interesting thing about slime mold?
\end{itemize}

\subsubsection{Success Criteria Importance}

The team has ranked the importance of each success criterion as follows:

\begin{itemize}
  \item Sending a message about human's impact on the environment: 4.25 / 5
  \item Making an entertaining game: 4.25 / 5
  \item Exploring SMA, sufficiently demonstrating its complexity: 3.75 / 5
  \item Making a game product that meets business requirements of conventional gamers: 3 / 5
  \item Conveying the emotions we intend to convey: 4 / 5
\end{itemize}


\section{Appendix — Reflection}

1. What went well while writing this deliverable?

2. What pain points did you experience during this deliverable, and how did you resolve them?

3. What knowledge and skills will the team collectively need to acquire to successfully complete the verification and validation of your project? Examples of possible knowledge and skills include dynamic testing knowledge, static testing knowledge, specific tool usage, Valgrind etc. You should look to identify at least one item for each team member.

4. For each of the knowledge areas and skills identified in the previous question, what are at least two approaches to acquiring the knowledge or mastering the skill? Of the identified approaches, which will each team member pursue, and why did they make this choice?

Felix Hurst

1. It was easy to determine our project's goals, as our team had just recently met with our supervisors and are in agreement about the direction we want to take our development as well as our verification and validation processes.

2. There were some setbacks due to many of our team members devoting time to midterm examinations. In addition, some sections required previous sections to be filled out first before they could be finished. These issues were resolved through effective communication and time management.

3. I will need to learn about how to interpret the results from surveys, as they can be ambiguous and difficult to understand, due to their often qualitative nature rather than quantitative. This is important for gauging usability, which will be done through surveys.

\begin{itemize}
  \item 4. Two approaches to acquiring this knowledge include:
\end{itemize}

-- Running a practice survey among our team and attempting to interpret the results

-- Reading texts online that describe how to interpret survey data

I will pursue the first approach, as I believe a first--hand experience would be more effective for my learning, and could also give us useful insights about our own project.

BoWen Liu

1. What went well while writing this deliverable?

Identifying the testing methodology and steps for each requirement went well due to our group having a solid grasp of how we want to implement the features.

2. What pain points did you experience during this deliverable, and howdid you resolve them?

A pain point of this deliverable was deciding how we want to evaluate success in each test and as such we decided to implement a checklist type system for functional requirements as there are solid requirements and a questionnaire type system for nonfunctional requirements as it cannot solely be evaluated well with a checklist to express the nuances.

3. What knowledge and skills will the team collectively need to acquire to

successfully complete the verification and validation of your project?

Examples of possible knowledge and skills include dynamic testing

knowledge, static testing knowledge, specific tool usage, Valgrind etc.

You should look to identify at least one item for each team member.

Knowledge of BtoC testing was important in regards to the nature of our product which in addition to needing to work well also contains many qualitative aspects which requires deeper nuance and breadth in testing.

4. For each of the knowledge areas and skills identified in the previous

question, what are at least two approaches to acquiring the knowledge

or mastering the skill? Of the identified approaches, which will each

team member pursue, and why did they make this choice?

An approach to understanding and improving knowledge on BtoC testing is continuous feedback from peers and the market in terms of continuous product development. Another approach to acquiring said knowledge is to do plenty of research online in regards to similar type and scale of videogame companies to understand their approaches

Marcos Hernandez--Rivero

1. What went well while writing this deliverable?

We generally already knew exactly what we wanted to write and how we wanted to approach this document in terms of “Where are we going with this”. On friday we had a meeting with our Capstone Supervisor so we were fresh from receiving feedback.

2. What pain points did you experience during this deliverable, and how did you resolve them?

For our type of project, we have a lot of aspects that are very hard to test. Stuff like the non--deterministic Slime Mold Algorithm, or having A LOT of non functional requirements means figuring out ways to test all of this is very hard. We resolved this by meeting as a team and brainstorming possible ways to solve this, but that could not get us all the way there for some things. Another pain point was that there were quite a few dependencies in this document, with some parts being uncompletable until other people completed a specific part. That combined with the previous week being super busy due to midterms, assignments, etc means we were not able to dedicate as much time to this as we would have liked. This was mostly resolved by simply doing it on the weekend/on monday

3. What knowledge and skills will the team collectively need to acquire to successfully complete the verification and validation of your project? Examples of possible knowledge and skills include dynamic testing knowledge, static testing knowledge, specific tool usage, Valgrind etc. You should look to identify at least one item for each team member.

I will need to learn about dynamic testing, as many issues do not occur statically when each section is separate, but rather once the code is running and all the aspects of the projects are combined. I need to be able to determine how to troubleshoot, test, and fix issues when they appear in live runs.

4. For each of the knowledge areas and skills identified in the previous question, what are at least two approaches to acquiring the knowledge or mastering the skill? Of the identified approaches, which will each team member pursue, and why did they make this choice?

I see two main paths to obtain and practice this skill. The first one is simply watching videos and documentation on dynamic testing, especially for video games, which is likely to help somewhat but also very prone to being out of scope for our project depending on the contents of the document. The second approach I see is going through old projects (or prototypes for this project) and running dynamic testing by fault injection, where I manually add errors into the code so when the program runs something will be wrong, then I can determine if my dynamic testing skills can catch it. I feel like I will likely go with option 2, although having option 1 as a supplement is also beneficial.

Andy Liang

1. I set up a tight Req→Test→Evidence traceability view that exposed gaps early and kept Section 6 internally consistent. I also translated subjective non--functional requirements into measurable thresholds (e.g., viewing distance, contrast ratio, legibility size) and centralized symbolic parameters (Sec. 6.1) so all tests referenced the same constants.

2. Defining objective oracles for behaviors that shouldn’t assert exact paths and for UX that felt subjective was difficult. I resolved this by using seedable, property--based checks with acceptance envelopes (reach target within N steps, avoid forbidden cells, show monotonic progress) and by writing operational UX definitions (distance, contrast, error rate) that became pass/fail criteria in our checklists and questionnaires, with snapshot logs for run--to--run diffs.

3. I will need to learn writing testable requirements and accessibility verification (contrast/legibility, cue redundancy).

4. I will (a) run a “requirement clinic” pass to make statements measurable and (b) build an accessibility checklist—I will do (a) first to lock clarity, then (b) to keep UX tests objective.

\end{document}

