
\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}

\input{../../Common}

\begin{document}

\title{Usability Report for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{5cm}p{2cm}X}
\toprule {\bf Author} & {\bf Version}& {\bf Date}\\
\midrule
All & 1.0 & March 5, 2026\\
Felix Hurst & 1.1 & March 7, 2026\\
\bottomrule
\end{tabularx}

\newpage

\tableofcontents
%\newpage
%\listoftables
\newpage

\pagenumbering{arabic}

% For this report follow the HCI course. The usability testing has to be systematic,
% rigorous and quantified. You should have a clear plan for the usability testing,
% including the goals of the testing, the specific tasks you ask users to complete,
% the specific questions you ask users, the specific survey you ask the users to complete, etc.

This document will report on and discuss the results of the Usability Survey.

\section{General Information}
The Usability Survey was conducted by deploying a demo build of our project
executable, and distributing it to our stakeholders, our players. They were asked
to play our game and then submit a survey to tell us about their experience.

For a list of the questions found in the Usability Survey, refer to the
\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/VnVPlan/VnVPlan.pdf}{VnV Plan} document.

This report is also closely tied with our
\href{https://github.com/felix-hurst/Ad-Natura/blob/main/docs/VnVReport/VnVReport.pdf}{Verification and Validation Report},
as this report serves to determine the level of validation we have with our stakeholders.

\section{Usability Survey Results}
This section will report a summary of the results from each major section
of the survey form. This survey was conducted from March 4th to March 7th, 2026.

\subsection{Performance Report}
Reported average frame rates ranged from 12.80 fps to 35.44 fps,
resulting in an overall average of 23.8 fps. This is not ideal,
as we were aiming for an overall average of at least 30 fps,
though it is still playable and will not harm the experience by
a lot, especially considering our pixel art style.

\subsection{Demographics}
The people who participated in the survey included a mix of North
Americans and Europeans. They were aged 22+ and predominantly male.
Most preferred the genres of Action and RPG. There were many different
themes enjoyed by responders.

\subsection{Learnability}
Participants played the game for 5--20 minutes before finishing or
deciding to submit the survey. The basic controls were learned quickly,
however, the game mechanics were not very intuitive to the player.
The water ball tool was understood best, and the destructive ball tool
was confusing. Responders indicated a need for stronger indicators and
tutorials for basic mechanics, such as a menu explaining the control
scheme, improved visual feedback for correct actions, and more
obvious usage for the tools. In particular, the destructive ball tool
currently looks too much like a fireball, and gives the wrong impression
of how to use it, with players trying to vaporize water or burn wood
rather than destroy the breakable stone objects. Overall, responders
thought the puzzles were a bit too difficult to overcome.

\subsection{Entertainment Value}
Participants enjoyed the visual aspects of the game, including the
slime mold's movement, the art style and environment, the player
animations and aiming of the tools, and the water splashing.
Players had frustration with the lack of clarity in certain game
mechanics, such as the ammo system, uncontrollable nature of
the slime mold, and overall lack of direction for the puzzles.
In particular, the wall climbing section at the end of the level
was considered the least entertaining game mechanic.

\subsection{Business Requirements}
We received mixed ratings for the business requirements of the
project. No one experienced game freezes, crashes, and other
similar software exceptions. However, there were a mix of high
and low ratings for whether the game was worth their time.

\subsection{Story / Message}
Most participants felt that the demo was too short to discern
a story or message from it, but a few responders did catch on to
exactly what we were intending to present in terms of story: The
ideas of working with nature instead of against it, and avoiding
interjecting man-made items and waste into the environment.

\subsection{Emotions}
There were a mix of emotions that participants experienced. Those that
struggled with the game mechanics felt confusion and irritation,
and others felt intrigue and curiosity, as well as accomplishment
when solving puzzles. A particular moment of emotion happened when
players figured out they could break the stone objects to expose
water sources, serving as an ``Aha!" moment.

\subsection{Exploring the Slime Mold Algorithm}
Most participants learned that the slime mold is attracted to water.
They indicated the game does not make the slime mold's mechanics
clear, but it does behave in a natural and unpredictable manner.
A responder suggested adding something trying to harm the slime mold,
as a means of eliciting empathy from the player. Another responder
wondered why the slime mold was even present in the world.
Some responders enjoyed the slime mold's pulsing visual and unique
concept.

\section{Discussion of Survey Results}
It is clear that our project in its current state is lacking a lot
of key elements that make a game fun to play. Currently, the game
does not give the player instructions or tutorials, and as a result,
the game is confusing and frustrating to learn. This led to low levels
of engagement, where players mostly looked to the visual aspects for
enjoyment. However, we did succeed in part in sending the message we
intended to send, eliciting feelings of curiosity and intrigue,
and teaching the player of some aspects of the slime mold.

\section{Changes Due To Results}
Our next major focus should be on introducing proper menus and
tutorials to the game, explaining to the player what they can do
with their tools, and give them hints on how to overcome puzzles.
This will be accomplished through the in-game journal logs, which
will aid in both teaching the player how to play, and telling
the story of the game. Additionally, we will consider some feedback
from the respondents involving specific visual feedback improvements
for the slime mold's behaviour and mechanics, and we will work on
further optimizing the game's performance wherever possible.

We plan on running a second Usability Survey in late March after
making improvements to the project, so that we may measure our
success again and compare our results to our past results, to
see how much we succeeded in improving the project.

\end{document}
